Viscous Transport in Eroding Porous Media

### 2019-08-27 docs/transport/erosion_transport.tex
finished up a first draft for section 6.2

\todo[inline]{Nothing about the anomalous dispersion rate here}
At high porosities, the dispersion rate is close to 1, and this can be
caused by one of two reasons.  1) There is no measurable anomalous
dispersion; or, 2) The streamlines are too short to see the anomalous
dispersion.

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/20b_second_moment_long_ref}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20Transport} (a): The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
The dash line is the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with
$p=0.2064$, and the corresponding root-mean-square error is $5.9 \times
10^{-3}$. (b): The temporal evolution of $\sigma_\lambda$ as a function
of time at seven different porosities.  The dashed, which has slope one,
corresponds to $\sigma_\lambda$ if no bodies were present.  At early
times, the particles undergo a ballistic motion, but once they have
traversed a few grains, the dispersion becomes super-dispersive.  The
dashed-dotted lines are lines of best fit with slopes $1.0644$
($\phi=95.1\%$), $1.0673$ ($\phi=85.09\%$), $1.0594$ ($\phi=75.15\%$),
$0.9664$ ($\phi=65.09\%$), $0.7766$ ($\phi=55.10\%$), $0.7475$
($\phi=45.08\%$), and $0.5607$ ($\phi=37.68\%$).}
\end{figure}

>>>>

In Figure~\ref{fig:Eroding20Transport}(b), we plot the temporal
evolution of the particle spreading $\sigma_\lambda$.  The spreading is
computed at several geometries that are formed during the erosion
process.  So that the spreading reaches a statistical equilibrium, we
use the reinsertion algorithm described in Section~\ref{sec:dispersion}
to form sufficiently long trajectories.  For all the reported
porosities, the particle dispersion exhibits two power low regimes.
Initially, the dispersion is ballistic ($\sigma_\lambda \sim t$) since
individual fluid particles have not yet explored enough space to
significantly alter their velocity.  However, once the particles have
been subjected to a range of velocities, their dispersion slows down,
and we observe super-diffusive ($\sigma_\lambda \sim t^\alpha$, $\alpha
\in (1/2,1)$) behavior over at least one order of magnitude in time.
Before any erosion takes place, the anomalous dispersion coefficient is
$\alpha = 0.56$.  Then, as the bodies begin to erode, the dispersion
rate grows towards the ballistic regime that corresponds to the absence
of bodies.  The monotonic increase in dispersion with respect to the
porosity is explained by the onset of channels where many tracers
experience less variability in their velocities.

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/20b_second_moment_long_ref}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20Transport} (a): The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
The dash line is the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with
$p=0.2064$, and the corresponding root-mean-square error is $5.9 \times
10^{-3}$. (b): The temporal evolution of $\sigma_\lambda$ as a function
of time at seven different porosities.  The dashed, which has slope one,
corresponds to $\sigma_\lambda \sim t$ if no bodies were present.  At
early times, the particles undergo a ballistic motion, but once they
have traversed a few grains, the dispersion becomes super-dispersive
with $\sigma_\lambda \sim t^\alpha$, $\alpha \in (1/2,1)$.  The
dashed-dotted lines are lines of best fit with slopes $\alpha = 1.06$
($\phi=95.1\%$), $\alpha = 1.07$ ($\phi=85.09\%$), $\alpha = 1.06$
($\phi=75.15\%$), $\alpha = 0.97$ ($\phi=65.09\%$), $\alpha = 0.78$
($\phi=55.10\%$), $\alpha = 0.75$ ($\phi=45.08\%$), and $\alpha = 0.56$
($\phi=37.68\%$).  Values greater than 1 are a result of using a
least-squares fit for the tails of the particle spreading.}
\end{figure}
